---
title: "Searching Citations on Google Scholar"
author: "Benjamin Guinaudeau"
date: "18. November 2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this example, I use `tidybrowse` to set up a docker container on which a selenium server is running. Selenium emulate a web-browser (here Chrome) and allows you to navigate websites as if you were a real user. Thanks to selenium, you can overcome many limitations of `rvest` and scrape websites which use javascript in the background. 

In this example, I navigate google scholar and automatically extract citations and the BibTex files.

## Background

Recently, I worked on an academic project with a colleague, who was not fluent in latex or markdown. We relied on the usual common denominator: MS Word. While editing the manuscript, we manually added references at the end of the document using APA-Style citations. But, when we were about to submit the paper to a journal, we realized that Chicago citation-style was required. 

Instead of manually editing each of the references, I wrote this small script, which does two things: 
1. Search on google scholar for any query (DOI, Citation, Author, etc...)
2. Save the clean citations proposed by scholar (APA, ISO 609 and MLA) as well as the underlying BibTex file.


## Packages

```{r, message = F}
library(tidybrowse)
```

## A couple of helpers

```{r}

# Navigate to google scholar page
go_to_citation <- function(chrome, citation){
  
  # Create query
  query <- glue::glue('https://scholar.google.com/scholar?hl=fr&as_sdt=0%2C5&q={stringr::str_replace_all(citation, "\\\\s+", "+")}&btnG=')
  
  # Navigate to url
  chrome %>% go(query)
  Sys.sleep(.5)
  
  # Happens once every session
  # you need to solve the captcha and it will not come back
  while(tidyselenium::check_element(chrome, '#gs_captcha_c')){
    message("Solve the captcha in the VNC window\nWaiting 20 seconds")
    Sys.sleep(20)
    # readline("Before continuing, you need to solve a captcha in the VNC window.
    #         Once you're done, press 'enter'")
  }
  
  # Find all citations button
  elems <- chrome %>%
    tidyselenium::elements('*[role="button"]') %>%
    tidyselenium::filter.webElement("title", "Citer") 
  
  # Click the button (or the first one if several results are provided)
  if(length(elems) > 1) elems <- elems[[1]]
  elems %>% tidyselenium::click() 
  
  return(chrome)
}


# Access the three proposed citations and the bibtex info
get_citation_info <- function(chrome){
  
  # Get proposed citations
  cites <- chrome %>%
    tidyselenium::elements(".gs_citr") %>%
    purrr::map_chr(get_text)
  
  # Find link to BibTex file
  link <- chrome %>%
    tidyselenium::elements("*[href]") %>%
    purrr::map_chr(tidyselenium::get_attribute, "href") %>%
    stringr::str_subset("scholar.bib")
  
  # Read BibText file
  bib <- try(paste(readLines(link), collapse = "\n"))
  
  if(inherits(bib, "try-error")){
    bib <- paste(readLines(link), collapse = "\n")
  }
  
  return(list(cites = cites, bib = bib))
  
}

# Parse the results and returns a tibble
parse_gs_res <- function(gs_res){
  gs_res$cites %>% 
    purrr::map2_dfc(c("apa", "iso_690", "mla"), ~tibble::tibble(.x) %>% purrr::set_names(.y)) %>%
    dplyr::mutate(bib = gs_res$bib)
}

```

## Init docker container

You need a running docker daemon in the background. For this, docker must be installed and the docker daemon must be started. 

```{r, warning = F}
# This function will create/start a container named "chrome" and 
# returns a Selenium Driver object associated with this container
chrome <- tidyselenium::chrome_init("chrome", view = F)
```

Scraping is really easier if you can observe what is happening under the hood. Hence, the container also hosts a vnc server, that allows you to view and interact in real time with the emulated browser. 

```{r, eval = F}
# This opens vnc viewer and displays the selenium browser
dockeR::view_container("chrome")
# To know the port used by the vnc server run:
# dockeR::get_port("chrome", 5900)
```


## Read citations

For this example, I simly some references from the word document into `citation.txt`. Each row corresponds to one full-text citation, but you could paste any kind of keywords (DOI, Author, Keyword, etc...).

```{r}
word_citation <- readLines("citation.txt") %>%
  dplyr::glimpse()
```

## Scraping

```{r}
# Open a new window on selenium container
chrome %>%
  tidyselenium::new_window()

citation_dt <- word_citation %>% 
  purrr::map_dfr(~{
    cli::cli_alert_info(.x)
    
    out <- try({
      chrome %>%
        go_to_citation(.x) %>%
        get_citation_info 
    })
    
    if(inherits(out, "try-error")){
      
      cli::cli_alert_danger("Could not retrieve citation")
      return(tibble::tibble())
      
    } else {
      
      cat(out$bib)
      message("\n\n")
      return(parse_gs_res(out))
      
      Sys.sleep(2)
      
    }
  }) %>%
  dplyr::glimpse()

# Close all opened windows
chrome %>%
  tidyselenium::close_all()

```

## Export as .bib

You can now write a bibtex file and use it in a latex document. 
For markdown users, I've just discovered that you can cite all your bibliography by adapting the yaml-header ([More info](https://github.com/rstudio/rmarkdown/issues/1096)).

```{r}

citation_dt$bib %>%
  paste(collapse = "\n\n") %>%
  readr::write_lines("mandate.bib")

```

## Read proposed citation

Google scholar proposed three citation format. You can also print them and directly copy them back into the word document. 

```{r}

citation_dt$mla %>%
  sort %>%
  paste(collapse = "\n\n") %>%
  cat

```

