---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidybrowser

<!-- badges: start -->
<!-- badges: end -->

Tidybrowser is a meta package containing different packages easing web scrapping and the deployment of docker containers from R. 

## Installation

``` r
# install.packages("devtools")
devtools::install.packages("benjaminguinaudeau/tidybrowser")
```

## Packages

### dockeR

dockeR wraps up docker command line tools and allows to manage docker containers from R. It can be use to deploy selenium servers, shiny-app servers, rstudio-servers, etc...

### tidyselenium

This wraps up RSelenium function in a pipable way. It also offers function to easily communicate with a selenium server running inside a docker container. 

### tidyweb

Tidyweb allows to represent xml-tree data in a tidy way. It works as well with xml-nodes as with selenium elements. 

### selinput

Selinput wraps up the python library pyautogui, which emulates mouse and keyboard input. It allows to easily type, click and scroll inside a docker container, with a running selenium server. 

### bashR

bashR allows to run some simple bash functions from whithin R.

```{r}
library(tidybrowser)
```

